Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-31 paper.tex
Move around intro a bit

@@

If numerical models are validated with physical model data that was obtained at
insufficiently high Reynolds numbers, it cannot be determined whether problems
with model predictions are caused by Reynolds number effects, other turbine
geometrical or operating parameters, or issues with the numerical model itself.
One might also obtain different predictions for scaled systems due to modified
physics at lower Reynolds numbers, e.g., laminar boundary layers and
transitional flow regimes. If the numerical model is then considered
``validated,'' there is a risk that its application at full-scale may produce
incorrect predictions. As such, it is questionable whether numerical models
validated with physical model data obtained at Reynolds numbers orders of
magnitude away from prototype scale should be considered validated at all.

>>>>

If numerical models are validated with physical model data that was obtained at
insufficiently high Reynolds numbers, it cannot be determined whether problems
with model predictions matching full scale observations are caused by Reynolds
number effects or issues with the numerical model itself. One might also obtain
different predictions for scaled systems due to modified physics at lower
Reynolds numbers, e.g., laminar boundary layers and transitional flow regimes.
If the numerical model is then considered ``validated,'' there is a risk that
its application at full-scale may produce incorrect predictions. As such, it is
questionable whether numerical models validated with physical model data
obtained at Reynolds numbers orders of magnitude away from prototype scale
should be considered validated at all.

@@
